Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-23 Scripts/Initial_Analysis.Rmd
First discussion draft

###### Just mean time

```{r vulnerabillity_index, eval = T}

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,fishing_entity_id,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  ) %>% 
  filter(
    tresh == "Tresh_one",
    metric == "mean_yr"
  )

Value_map_data <- Eme_value_data %>% 
  left_join(Total_value,
            by = c("fishing_entity_id","variable")) %>% 
  mutate(participation = (sum_value/tot_value)*100) %>% 
  filter(
    tresh == "Tresh_one",
    variable == "value"
  )

@@

Index_data <- Eez_d_hist %>% 
  left_join(Value_map_data) %>% 
  mutate(
    index = (participation/value),
    index = ifelse(is.na(index),0,index)
  ) %>% 
  select(1:3,value,participation,index,everything())

@@

Index_data <- Index_data %>% 
  mutate(
    index = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  )

Value_map_data <- Index_data %>% 
  select(sau_fishing_entity,fishing_entity_id,tresh,variable,participation = indexb)

>>>>

###### Mean ToE and vulnerabillity Index

@@

Index_data <- Eez_d_hist %>% 
  left_join(Value_map_data) %>% 
  filter(
    tresh == "Tresh_one",
    metric == "mean_yr"
  ) %>% 
  group_by(sau_fishing_entity,variable) %>% 
  summarise(
    toe = mean(value,na.rm=T),
    # sum_value = sum(sum_value),
    mean_part = mean(participation,na.rm=T)
  ) %>% 
  filter(!is.na(variable)) %>% 
  # spread(variable,sum_value) %>% 
  spread(variable,mean_part) %>% 
  mutate(
    imp = catch+value,
    index = imp/toe
  )

@@

Index_data <- Index_data %>% 
  mutate(
    index_norm =(index-min_index)/(max_index-min_index),
    index_2000 = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  )

### Explore index ####

ggplot(data = Index_data) +
  geom_point(
    aes(
      x = toe,
      y = imp,
      color = index_2000
    ),
    size = 4
  ) +
   scale_color_viridis(option="magma", discrete = F)

#### ------------  ####

Value_map_data <- Index_data %>% 
  select(sau_fishing_entity,fishing_entity_id,tresh,variable,participation = index)
